---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# shoe3d

<!-- badges: start -->
<!-- badges: end -->

[Documentation](https://srvanderplas.github.io/shoe3d)

## Data Source

The shoe data is located at `\\iastate.edu\lss\research\csafe-shoeprints`. For users on VPN or using personal devices, the \\iastate.edu\lss path may not work. In that case, replace it with \\las-dfs-01.las.iastate.edu\lss (for example Shoe data would become \\las-dfs-01.las.iastate.edu\lss\research\csafe-shoeprints).

To start with, I copied `005*` and `002*` left shoe stl files into `data-raw/`

```{r eval = F}
#usethis::use_data_raw() # set up directory

# this is the file path on bigfoot, but it won't work on windows (or a personal machine).
#mounting smb:

#install.packages("curl")
#this still isnt working? Email CSSM and waiting for their response 
require("curl")
handle <- new_handle()
handle_setopt(handle, username = "eblagg")
handle_setopt(handle, password = "") # If needed
request <- curl_fetch_memory("smb://las-dfs-01.las.iastate.edu/lss/research/csafe-shoeprints/ShoeImagingPermanent", handle = handle)
contents <- rawToChar(request$content)

lss_location <- file.path("smb://las-dfs-01.las.iastate.edu","/lss", "research","csafe-shoeprints", "ShoeImagingPermanent") 

# Copy the relevant files
file.copy(from = list.files(lss_location, "0[48]\\d{3}[L].*\\.stl", full.names = T), to = "data-raw/", overwrite = F)
```

These files can't be added to github - they're too big. I've modified `data-raw/.gitignore` to try to ensure that stl files aren't monitored by git (at least by default). 



## Other Details:
Please note that the 'shoe3d' project is released with a
[Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.