---
title: "Practice shoe"
author: "Heike"
date: "10/25/2019"
output: html_document
---



```{r setup}
#library(shoe3d)
library(tidyverse)
library(rgl)
library(Rvcg) # package for working with 3d meshes in R
library(Morpho) 
library(Arothron)
#library(MBA) # Spline regression
knitr::opts_chunk$set(cache = T)
```

Importing the shoes: (Using this since the shoes do not follow the same format as shoe grab)
```{r}
stl_new <- list.files("../data-raw/My_Scans", pattern = ".stl", full.names = T)
stl_file_path1 <- stl_new[str_detect(stl_new, "SonyL")][1]
sony1 <- Rvcg::vcgImport(stl_file_path1, clean = T)
sony1<-Arothron::trasf.mesh(sony1, barycenter = Arothron::bary.mesh(sony1))
stl_file_path2 <- stl_new[str_detect(stl_new, "SonyL")][3]
sony2 <- Rvcg::vcgImport(stl_file_path2, clean = T)
sony2<-Arothron::trasf.mesh(sony2, barycenter = Arothron::bary.mesh(sony2))
```

# get barycenter from meshes and move meshes into bary center
```{r}
center3d <- function(mesh, method=barycenter) {
  bary <- method(mesh) %>% colMeans()
  translate3d(mesh, -bary[1], -bary[2], -bary[3])
}

sony1c <- center3d(sony1)
sony2c <- center3d(sony2)

rgl::plot3d(sony2c, aspect="iso", col="blue", add=TRUE)
rgl::plot3d(sony1c, aspect="iso", col="green", add=TRUE)
axes3d()


```

# 3d point cloud from mesh
```{r}
sony1shoe<-shoe_coord(sony1)
sony2shoe<-shoe_coord(sony2)
```
# rotation matrices based on coordinates

```{r}
sony1pca<-prcomp(sony1shoe, center = TRUE,scale. = FALSE)
sony2pca<-prcomp(sony2shoe, center = TRUE,scale. = FALSE)
```


```{r}
#FIND A CENTERING??
sony1tran<-transform3d(sony1c, matrix = rotationMatrix(matrix = sony1pca$rotation))
sony2tran<-transform3d(sony2c, matrix =rotationMatrix(matrix = sony2pca$rotation))
```

```{r}
# rotate first scan into pc1, pc2, pc3
#rgl::plot3d(sony1c, aspect="iso", col="blue", add=TRUE)
rgl::plot3d(sony1tran, aspect="iso", col="red", add=TRUE)

# rotate second scan into pc1, pc2, pc3
#rgl::plot3d(sony2c, aspect="iso", col="green", add=TRUE)
rgl::plot3d(sony2tran, aspect="iso", col="red", add=TRUE)
#axes3d()

# rotated scans
#rgl::plot3d(sony1tran, aspect="iso", col="blue", add=TRUE)
#rgl::plot3d(sony2tran, aspect="iso", col="green", add=TRUE)
axes3d()

```


# check rotated points for minimal RMSE

```{r}
rotations <- list(
  rotationMatrix(matrix=diag(c(1,1,1))),
  rotationMatrix(matrix=diag(c(-1,1,1))),
  rotationMatrix(matrix=diag(c(1,-1,1))),
  rotationMatrix(matrix=diag(c(1,1,-1))),
  rotationMatrix(matrix=diag(c(1,-1,-1))),
  rotationMatrix(matrix=diag(c(-1,1,-1))),
  rotationMatrix(matrix=diag(c(-1,-1,1))),
  rotationMatrix(matrix=diag(c(-1,-1,-1)))
)
```

```{r}
#rgl::plot3d(sony2tran, aspect="iso", col="blue", add=TRUE)
#axes3d()
#rgl::plot3d(transform3d(sony1tran, matrix = rotations[[2]]), aspect="iso", col="green", add=TRUE)
#rgl::plot3d(transform3d(sony1tran, matrix = rotations[[3]]), aspect="iso", col="darkgreen", add=TRUE)
#rgl::plot3d(transform3d(sony1tran, matrix = rotations[[4]]), aspect="iso", col="cyan", add=TRUE) # this is the one


# july scan compared to first
rgl::plot3d(transform3d(sony2tran, matrix = rotations[[2]]), aspect="iso", col="blue", add=TRUE)
axes3d()
#rgl::plot3d(transform3d(sony1tran, matrix = rotations[[2]]), aspect="iso", col="green", add=TRUE)
rgl::plot3d(transform3d(sony1tran, matrix = rotations[[3]]), aspect="iso", col="cyan", add=TRUE) # this one
#rgl::plot3d(transform3d(sony1tran, matrix = rotations[[4]]), aspect="iso", col="darkgreen", add=TRUE) 


```


# comparison to aligning with Morpho pca

```{r}
shoeing<-pcAlign(sony1,sony2)
```

```{r}
rgl::plot3d(sony2, aspect="iso", col="blue", add=TRUE)
axes3d()
rgl::plot3d(shoeing, aspect="iso", col="green", add=TRUE)
```

Maybe interesting:
https://courses.cs.washington.edu/courses/cse577/11au/notes/Z12.pdf

https://stackoverflow.com/questions/9065156/how-to-align-two-meshes


# ICP using the already PC aligned shoes 

```{r}
scan1<-transform3d(sony2tran, matrix = rotations[[2]])
scan2<-transform3d(sony1tran, matrix = rotations[[3]])
```


```{r}
#checking to see that i chose the right rotations 
rgl::plot3d(scan1, aspect="iso", col="cyan", add=TRUE) 
rgl::plot3d(scan2, aspect="iso", col="blue", add=TRUE) 

```



```{r}
testa<-icp(scan1, scan2, iterations = 100)
```

```{r}
#ICP1.png  ICP2.png and ICPzoom.png
#rgl::plot3d(scan1, aspect="iso", col="cyan", add=TRUE) 
rgl::plot3d(scan2, aspect="iso", col="blue", add=TRUE) 
rgl::plot3d(testa, aspect="iso", col="red", add=TRUE)
axes3d()
```


##fewer points 

```{r}
scan1fewpoints<-data.frame(shoe_coord(scan1, verts = 6))
scan2fewpoints<-data.frame(shoe_coord(scan2, verts = 6))
```


```{r}
N<-nrow(scan1fewpoints)
indices <- c( seq(1,N,by=1))
fewerpoints1<-tmesh3d(as.matrix(scan1fewpoints),indices = indices)
```

#planear 


```{r}

```


