---
title: "Practice shoe"
author: "Heike"
date: "10/25/2019"
output: html_document
---



```{r setup}
#library(shoe3d)
library(tidyverse)
library(rgl)
library(Rvcg) # package for working with 3d meshes in R
library(Morpho) 
library(Arothron)
#library(MBA) # Spline regression
knitr::opts_chunk$set(cache = T)
```

Importing the shoes: (Using this since the shoes do not follow the same format as shoe grab)
```{r}
stl_new <- list.files("../data-raw/My_Scans", pattern = ".stl", full.names = T)
stl_file_path1 <- stl_new[str_detect(stl_new, "SonyL")][1]
sony1 <- Rvcg::vcgImport(stl_file_path1, clean = T)
sony1<-Arothron::trasf.mesh(sony1, barycenter = Arothron::bary.mesh(sony1))
stl_file_path2 <- stl_new[str_detect(stl_new, "SonyL")][3]
sony2 <- Rvcg::vcgImport(stl_file_path2, clean = T)
sony2<-Arothron::trasf.mesh(sony2, barycenter = Arothron::bary.mesh(sony2))
```


#All sony L shoes 
```{r}
#1
stl_new <- list.files("../data-raw/My_Scans", pattern = ".stl", full.names = T)
stl_file_path1 <- stl_new[str_detect(stl_new, "SonyL")][1]
sony1 <- Rvcg::vcgImport(stl_file_path1, clean = T)

#2
stl_file_path2 <- stl_new[str_detect(stl_new, "SonyL")][2]
sony2 <- Rvcg::vcgImport(stl_file_path2, clean = T)

#3
stl_file_path3 <- stl_new[str_detect(stl_new, "SonyL")][3]
sony3 <- Rvcg::vcgImport(stl_file_path3, clean = T)

#4
stl_file_path4 <- stl_new[str_detect(stl_new, "SonyL")][4]
sony4 <- Rvcg::vcgImport(stl_file_path4, clean = T)

#5
stl_file_path5 <- stl_new[str_detect(stl_new, "SonyL")][5]
sony5 <- Rvcg::vcgImport(stl_file_path5, clean = T)

#6
stl_file_path6 <- stl_new[str_detect(stl_new, "SonyL")][6]
sony6 <- Rvcg::vcgImport(stl_file_path6, clean = T)

```






# get barycenter from meshes and move meshes into bary center
```{r}
center3d <- function(mesh, method=barycenter) {
  bary <- method(mesh) %>% colMeans()
  translate3d(mesh, -bary[1], -bary[2], -bary[3])
}
```




```{r}
sony1c <- center3d(sony1)
sony2c <- center3d(sony2)
sony3c <- center3d(sony3)
sony4c <- center3d(sony4)
sony5c <- center3d(sony5)
sony6c <- center3d(sony6)
```

```{r}

rgl::plot3d(sony2c, aspect="iso", col="blue", add=TRUE)
rgl::plot3d(sony1c, aspect="iso", col="green", add=TRUE)
axes3d()


```

# 3d point cloud from mesh
```{r}
sony1shoe<-shoe_coord(sony1c)
#sony2shoe<-shoe_coord(sony2c)
#sony3shoe<-shoe_coord(sony3c)
#sony4shoe<-shoe_coord(sony4c)
#sony5shoe<-shoe_coord(sony5c)
#sony6shoe<-shoe_coord(sony6c)
```
# rotation matrices based on coordinates

```{r}
sony1pca<-prcomp(sony1shoe, center = TRUE,scale. = FALSE)
sony2pca<-prcomp(sony2shoe, center = TRUE,scale. = FALSE)
sony3pca<-prcomp(sony3shoe, center = TRUE,scale. = FALSE)
sony4pca<-prcomp(sony4shoe, center = TRUE,scale. = FALSE)
sony5pca<-prcomp(sony5shoe, center = TRUE,scale. = FALSE)
sony6pca<-prcomp(sony6shoe, center = TRUE,scale. = FALSE)
```


```{r}
#FIND A CENTERING??
sony1tran<-transform3d(sony1c, matrix = rotationMatrix(matrix = sony1pca$rotation))
sony2tran<-transform3d(sony2c, matrix =rotationMatrix(matrix = sony2pca$rotation))
sony3tran<-transform3d(sony3c, matrix = rotationMatrix(matrix = sony3pca$rotation))
sony4tran<-transform3d(sony4c, matrix =rotationMatrix(matrix = sony4pca$rotation))
sony5tran<-transform3d(sony5c, matrix = rotationMatrix(matrix = sony5pca$rotation))
sony6tran<-transform3d(sony6c, matrix =rotationMatrix(matrix = sony6pca$rotation))
```

```{r}
# rotate first scan into pc1, pc2, pc3
#rgl::plot3d(sony1c, aspect="iso", col="blue", add=TRUE)
rgl::plot3d(sony6tran, aspect="iso", col="red", add=TRUE)

# rotate second scan into pc1, pc2, pc3
#rgl::plot3d(sony2c, aspect="iso", col="green", add=TRUE)
#rgl::plot3d(sony2tran, aspect="iso", col="red", add=TRUE)
#axes3d()

# rotated scans
#rgl::plot3d(sony1tran, aspect="iso", col="blue", add=TRUE)
#rgl::plot3d(sony2tran, aspect="iso", col="green", add=TRUE)
axes3d()

```


# check rotated points for minimal RMSE

```{r}
rotations <- list(
  rotationMatrix(matrix=diag(c(1,1,1))),
  rotationMatrix(matrix=diag(c(-1,1,1))),
  rotationMatrix(matrix=diag(c(1,-1,1))),
  rotationMatrix(matrix=diag(c(1,1,-1))),
  rotationMatrix(matrix=diag(c(1,-1,-1))),
  rotationMatrix(matrix=diag(c(-1,1,-1))),
  rotationMatrix(matrix=diag(c(-1,-1,1))),
  rotationMatrix(matrix=diag(c(-1,-1,-1)))
)
```

```{r}
rgl::plot3d(scan6, aspect="iso", col="green", add=TRUE)
rgl::plot3d(transform3d(sony2tran, matrix = rotations[[7]]), aspect="iso", col="red", add=TRUE)
#rgl::plot3d(transform3d(sony6tran, matrix = rotations[[3]]), aspect="iso", col="darkgreen", add=TRUE)
#rgl::plot3d(transform3d(sony6tran, matrix = rotations[[4]]), aspect="iso", col="cyan", add=TRUE) # this is the one
#rgl::plot3d(transform3d(sony6tran, matrix = rotations[[5]]), aspect="iso", col="red", add=TRUE)
#rgl::plot3d(transform3d(sony6tran, matrix = rotations[[6]]), aspect="iso", col="yellow", add=TRUE)


# july scan compared to first
#rgl::plot3d(transform3d(sony2tran, matrix = rotations[[4]]), aspect="iso", col="blue", add=TRUE)
axes3d()
#rgl::plot3d(sony2tran, aspect="iso", col="green", add=TRUE)
#rgl::plot3d(transform3d(sony1tran, matrix = rotations[[3]]), aspect="iso", col="cyan", add=TRUE) # this one
#rgl::plot3d(transform3d(sony1tran, matrix = rotations[[4]]), aspect="iso", col="darkgreen", add=TRUE) 


```


# comparison to aligning with Morpho pca

```{r}
shoeing<-pcAlign(sony1,sony2)
```

```{r}
rgl::plot3d(sony2, aspect="iso", col="blue", add=TRUE)
axes3d()
rgl::plot3d(shoeing, aspect="iso", col="green", add=TRUE)
```

Maybe interesting:
https://courses.cs.washington.edu/courses/cse577/11au/notes/Z12.pdf

https://stackoverflow.com/questions/9065156/how-to-align-two-meshes


# ICP using the already PC aligned shoes 

```{r}
scan1<-transform3d(sony1tran, matrix = rotations[[8]])
scan2<-transform3d(sony2tran, matrix = rotations[[7]])
scan3<-transform3d(sony3tran, matrix = rotations[[4]])
scan4<-transform3d(sony4tran, matrix = rotations[[8]])
scan5<-transform3d(sony5tran, matrix = rotations[[5]])
scan6<-transform3d(sony6tran, matrix = rotations[[7]])
```


```{r}
#checking to see that i chose the right rotations 
rgl::plot3d(scan1, aspect="iso", col="yellow", add=TRUE) 
rgl::plot3d(scan2, aspect="iso", col="blue", add=TRUE) 
rgl::plot3d(scan3, aspect="iso", col="red", add=TRUE)
rgl::plot3d(scan4, aspect="iso", col="darkgreen", add=TRUE) 
rgl::plot3d(scan5, aspect="iso", col="green", add=TRUE)
rgl::plot3d(scan6, aspect="iso", col="orange", add=TRUE)
```


ONLY RUN IF YOU HAVE LOTS OF TIME TO KILL....... IT ABOUT KILLED MY POOR LAPTOP :)
```{r}
icp12<-icp(scan1, scan2, iterations = 100)
icp13<-icp(scan1, scan3, iterations = 100)
icp14<-icp(scan1, scan4, iterations = 100)
icp15<-icp(scan1, scan5, iterations = 100)
icp16<-icp(scan1, scan6, iterations = 100)
icp23<-icp(scan2, scan3, iterations = 100)
icp24<-icp(scan2, scan4, iterations = 100)
icp25<-icp(scan2, scan5, iterations = 100)
icp26<-icp(scan2, scan6, iterations = 100)
icp34<-icp(scan3, scan4, iterations = 100)
icp35<-icp(scan3, scan5, iterations = 100)
icp36<-icp(scan3, scan6, iterations = 100)
icp45<-icp(scan4, scan5, iterations = 100)
icp46<-icp(scan4, scan6, iterations = 100)
icp56<-icp(scan5, scan6, iterations = 100)
```

```{r}
icpothertest<-icp(scan1, scan6, iterations = 10)
```

```{r}
rgl::plot3d(scan1, aspect="iso", col="red", add=TRUE) 
rgl::plot3d(scan6, aspect="iso", col="green", add=TRUE) 
rgl::plot3d(icpothertest, aspect="iso", col="blue", add=TRUE) #this doesnt seem to be aligning correctly now 
```


The other way around: 
```{r}
icp21<-icp(scan2, scan1, iterations = 100)
icp31<-icp(scan3, scan1, iterations = 100)
icp41<-icp(scan4, scan1, iterations = 100)
icp51<-icp(scan5, scan1, iterations = 100)
icp61<-icp(scan6, scan1, iterations = 100)
icp32<-icp(scan3, scan2, iterations = 100)
icp42<-icp(scan4, scan2, iterations = 100)
icp52<-icp(scan5, scan2, iterations = 100)
icp62<-icp(scan6, scan2, iterations = 100)
icp43<-icp(scan4, scan3, iterations = 100)
icp53<-icp(scan5, scan3, iterations = 100)
icp63<-icp(scan6, scan3, iterations = 100)
icp54<-icp(scan5, scan4, iterations = 100)
icp64<-icp(scan6, scan4, iterations = 100)
icp65<-icp(scan6, scan5, iterations = 100)
```


```{r}
rgl::plot3d(scan1, aspect="iso", col="red", add=TRUE) 
rgl::plot3d(scan2, aspect="iso", col="green", add=TRUE) 
rgl::plot3d(icp12, aspect="iso", col="blue", add=TRUE) 
rgl::plot3d(icp21, aspect="iso", col="pink", add=TRUE) 
```


```{r}
res2<-icp_rev(scan1, scan2, iterations = 5)
testb <- res2$mesh
rgl::plot3d(testb, aspect="iso", col="red", add=TRUE)
rgl::plot3d(scan1, aspect="iso", col="blue", add=TRUE)
```






##fewer points 

```{r}
scan1fewpoints<-data.frame(shoe_coord(scan1, verts = 6))
scan2fewpoints<-data.frame(shoe_coord(scan2, verts = 6))
```


```{r}
N<-nrow(scan1fewpoints)
indices <- c( seq(1,N,by=1))
fewerpoints1<-tmesh3d(as.matrix(scan1fewpoints),indices = indices)
```

#planear 


```{r}
vertices <- c( 
     -1.0, -1.0,  1.0,
      1.0, -1.0,  1.0,
      1.0,  1.0,  1.0,
     1.0, -1.0, -1.0,
      1.0, -1.0, -1.0,
      1.0,  1.0, -1.0
  )
  indices <- c( 1, 2, 3, 4,5,6 )
  
  open3d()  
   wire3d(qmesh3d(vertices, indices) )
```

```{r}

```










New Sony 


```{r}
#Left
stl_new1 <- list.files("../data-raw/My_Scans", pattern = ".stl", full.names = T)
stl_file_pathnew <- stl_new1[str_detect(stl_new1, "eva")][1]
underam <- Rvcg::vcgImport(stl_file_pathnew, clean = T)

```

```{r}
rgl::plot3d(underam, aspect="iso", col="red", add=TRUE)
```



