---
title: "Shoe Alignment"
output: html_document
---

##The Alignment of shoes 

Note: For this alignment we will be assuming two things:
1) We have the full print of the shoe
2) A shoe is not going to change sizes from being worn. That is, a size 8 shoe, will always be a size 8 shoe. 

###Setup

First step is to set up a file path to the data folder. Then we want to look at the change overtime a specific shoe, so we need to grab the shoe scans over time. Using the function *shoe_grab* to grab the scans of a given shoe ID, specify the id number of a shoe you want to look at, (Make sure you have access to the data, follow the steps on the README for more information. For more information on the shoe data, see **Longituidinal_Shoe_Study**), and turns the given shoe into mesh objects to do further analysis. 

When specifing an scan date, the function will output a single shoe where as if scandate is NULL, the function will output a list of all of the shoes containing the specified id. Then you can call each shoe by referencing the specific shoe using [[i]]

For example
```{r}
shoe05<-shoe_grab(shoeid = "005772L", scandate = NULL ,filepath="../data-raw")
```
then pulling out a single shoe 

```{r}
shoe05_3<-shoe05[[1]][["stl"]][[3]]
```


###Alignment 

At first we wanted to try to simplify the mesh object to just the basic shape in order have simplicity when aligning, however the problem was realized that we are using a prediction to allign rather than the shoe, 


