---
title: "Shoe Alignment"
output: html_document
---
```{r setup, echo = T}
library(shoe3d)
```

## The Alignment of shoes 

Note: For this alignment we will be assuming two things:
1) We have the full print of the shoe
2) A shoe is not going to change sizes from being worn. That is, a size 8 shoe, will always be a size 8 shoe. 

### Setup

First step is to set up a file path to the data folder. Then we want to look at the change overtime a specific shoe, so we need to grab the shoe scans over time. Using the function *shoe_grab* to grab the scans of a given shoe ID, specify the id number of a shoe you want to look at, (Make sure you have access to the data, follow the steps on the README for more information. For more information on the shoe data, see **Longituidinal_Shoe_Study**), and turns the given shoe into mesh objects to do further analysis. 

When specifing an scan date, the function will output a single shoe where as if scandate is NULL, the function will output a list of all of the shoes containing the specified id. Then you can call each shoe by referencing the specific shoe using [[i]]

For example: 
```{r}
shoe05<-shoe_grab(shoeid = "005772L", scandate = NULL ,filepath="../data-raw")
```
then pulling out a single shoe 

```{r}
shoe05_3<-shoe05[[1]][["stl"]][[3]]
```

A triangle mesh object is made up of the following parts, sufaces, polygons, faces, edges and vertices.
(intert drawing)

### Alignment 

Some background: 
At first we wanted to try to simplify the mesh object to just the basic shape in order have simplicity when aligning, however the problem was realized that we are using a prediction to allign rather than the shoe. The next "attempt" at alignment came from a package called morph. (add information about morph). In order to use this package, we needed to transform the data from a mesh object into a plane of points. In order to do this, we greated the function *shoe_coord*. This function takes a triangle mesh object, and looks at the vertices that make up each triangle. With a specific amount of vertices specified using the specification vert, *shoe_coord*, takes these vertices and maps them onto a x,y,z coordinate plane. Then using this coordinate plane, the allignment process began. 

Principal Component Analysis: 
The basic idea of principal component analysis is to take a dataset with many variables, and simplify that dataset by turning the original variables into a smaller number of "Principal Components". These principal components are the underlying structure in the data. Taking that data and giving a vector in directions where there is the most variance. Taking these egienvectors as the data, we can get a "flattened" version of our origianl shoe. (this needs to be written better, future me problem, also have a graphic explaining it)

Once a shoe has been turned into coordinates from the verticies of a mesh object, we can use the function prcomp (site this and expain what it does) to get a transformation matrix. Some notes on this (I need to reword this but right now im being lazy):
-use vertices of 7 to decrease amount of points to match
-if you have too few points also doesnt work
-turn table works the best 
-Sony are the best matches 
-

An example: 





