---
title: "Shoe Alignment"
output: html_document
---

```{r setup, echo = T}
library(shoe3d)
```

## The Alignment of shoes 

Note: For this alignment we will be assuming two things:
1) We have the full print of the shoe
2) A shoe is not going to change sizes from being worn. That is, a size 8 shoe, will always be a size 8 shoe. 

### Setup

First step is to set up a file path to the data folder. Then we want to look at the change overtime a specific shoe, so we need to grab the shoe scans over time. Using the function *shoe_grab* to grab the scans of a given shoe ID, specify the id number of a shoe you want to look at, (Make sure you have access to the data, follow the steps on the README for more information. For more information on the shoe data, see **Longituidinal_Shoe_Study**), and turns the given shoe into mesh objects to do further analysis. 

When specifing an scan date, the function will output a single shoe where as if scandate is NULL, the function will output a list of all of the shoes containing the specified id. Then you can call each shoe by referencing the specific shoe using [[i]]

For example: 
```{r}
shoe05<-shoe_grab(shoeid = "005772L", scandate = NULL ,filepath="../data-raw")
```
then pulling out a single shoe 

```{r}

```

A triangle mesh object is made up of the following parts, sufaces, polygons, faces, edges and vertices.
(intert drawing)

### Alignment 

Some background: 
At first we wanted to try to simplify the mesh object to just the basic shape in order have simplicity when aligning, however the problem was realized that we are using a prediction to allign rather than the shoe. The next "attempt" at alignment came from a package called morph. (add information about morph). In order to use this package, we needed to transform the data from a mesh object into a plane of points. In order to do this, we greated the function *shoe_coord*. This function takes a triangle mesh object, and looks at the vertices that make up each triangle. With a specific amount of vertices specified using the specification vert, *shoe_coord*, takes these vertices and maps them onto a x,y,z coordinate plane. Then using this coordinate plane, the allignment process began. 

Principal Component Analysis: 
The basic idea of principal component analysis is to take a dataset with many variables, and simplify that dataset by turning the original variables into a smaller number of "Principal Components". These principal components are the underlying structure in the data. Taking that data and giving a vector in directions where there is the most variance. Taking these egienvectors as the data, we can get a "flattened" version of our origianl shoe. (this needs to be written better, future me problem, also have a graphic explaining it)

Once a shoe has been turned into coordinates from the verticies of a mesh object, we can use the function prcomp (site this and expain what it does) to get a transformation matrix. Some notes on this (I need to reword this but right now im being lazy):
-use vertices of 7 to decrease amount of points to match
-if you have too few points also doesnt work
-turn table works the best 
-Sony are the best matches 
-

An example: 








Once you have a rotation matrix from a principal component analysis, we need to turn the eclidean matrix into a homogeneous matrix in order to apply the given rotation to the orginal mesh3d object (so that surface areas can be compared rather than just the points of the verticies in the coordinate plane). 







#Measuring Distance


In order to find out how well our alignment is doing, we need to find the the distance between two different mesh objects. Because the points of a mesh object are arbitrarily chosen depending on the specified shoe scan. In order to correct for this we must find the closest point distance. To find this, we will be using the K-distance neighbor search, within each corresponding shoe made of a mesh object. K closest distance is measured in squared Euclidean distance.For two vectors (w_1,x_1,y_1,z_1) and (w_2,x_2,y_2,z_2), the euclidean distance is found by: 
      (w_1-w_2)^2+(x_1-x_2)^2+(y_1-y_2)^2+(z_1-z_2)^2
K-D construction is as follows divide the points in half by a line perpendicular to one of the axes, in each tree. Then recursively construct k-d trees for the two sets of points, the two points corresponding to the verticies of the triangles. Think of it as this, we first choose a shoe to be set. In this case shoe scan 1. Then for each one of the verticies of a triangle we draw a ball with radius \epsilon then we start espilon to be 0 and expand it till you hit the closest section with a specified point. Once that point is found, the distance is meausured and recorded. To impliment this method, the function vcgClostKD in the package Rvcg. Once these distances were found, we can extract specified quantiles of the distances in order to compare two shoe scan. For example, before any alignment, the range of distances between scan one and scan 2 was -98.45, and 65.24, however after pca alignment, we have the distance ranging from -11.05, to 29.45, this shows that the first step in our alignment is making a large difference in bringing the shoes closer together. We can then plot these differences using a color scale on the first shoe, where red represents a large difference between shoe scan 1 and shoe scan 2 in the positive direction and blue in the negative direction, and yellow/teal represents a small difference. The difference described numerically above can be seen in the two photos below. Here we see that without alignment, the shoes dramatically change distanced due to the angle they overlap by, (see some image above figure something), however when they are aligned, the distance changes slowly and shows the typical wear pattern areas in 
      



